Named Entity Recognition as Structured Prediction

### 2012-11-10 doc/report/paper.tex
++++methods

Named Entity Recognition (NER) is an information extraction task and has first been introduced as part of the 6th MUC (Sixth Message Understanding Conference)
that was focusing on the extraction of structured information from unstructured text, such as company names from newspaper articles \cite{nadeau2007survey}.
The most prominent types are generally known under the name of \emph{enamex} types, which are comprised of \texttt{Person Names}, 
\texttt{Organisations} and \texttt{Locations}. 
An additional type \texttt{Miscellaneous} captures names outside the classic \emph{enamax} type.
Apart from the above, there is also the \emph{timex} type, which covers date and time expressions and \emph{numex} for monetary values and percentages. 
Table \ref{table:NETypes} gives an overview of the different \namedentity (NE) types.

@@

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the CoNLL Shared Task 2002 \cite{tksintro} and 
the CoNLL Shared Task 2003 \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as Bio-tags that indicate the position in the Named Entity. %put in ``tokenized, chunked''
Our approach is based on \cite{strlearn}, the group that won the challenge for Spanish and Dutch in 2002.

@@

\section{Structured Prediction}
Prediction \cite{strlearn} is a supervised-learning approach, where a system uses training data to learn the prediction
of unseen data. It consequently maps an input \textbf{x} to an output \textbf{y}: \\

@@

\section{Implementation}

>>>>

Named Entity Recognition (NER) is an information extraction task and has first been introduced as part of the 6th MUC (Sixth Message Understanding Conference)
that was focusing on the extraction of structured information from unstructured text, such as company names from newspaper articles \cite{nadeau2007survey}.
The most prominent types are generally known under the name of \emph{enamex} types, which are comprised of \texttt{Person Names}, 
\texttt{Organisations} and \texttt{Locations}. 
An additional type \texttt{Miscellaneous} captures names outside the classic \emph{enamax} type.
Apart from the above, there is also the \emph{timex} type, which covers date and time expressions and \emph{numex} for monetary values and percentages. 
Table \ref{table:NETypes} gives an overview of the different Named Entity (NE) types.

@@

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the CoNLL Shared Task 2002 \cite{tksintro} and 
the CoNLL Shared Task 2003 \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as Bio-tags that indicate the position in the Named Entity. %put in ``tokenized, chunked''
Our approach is based on \cite{strlearn}, of the group that won the challenge for Spanish and Dutch in 2002.

@@

\section{Structured Prediction}
Prediction \cite{Taskar:2005:LSP:1102351.1102464} is a supervised-learning approach, where a system uses training data to learn the prediction
of unseen data. It consequently maps an input \textbf{x} to an output \textbf{y}: \\

@@

\section{Implementation}
In this section, we describe our implementation, the learning and decoding algorithm and the features.
